Descriptive_Stats

### 2023-05-31 Code/RankComparison.Rmd
Added section about removing heats from ranked based comparison for 2019vs2022

>>>>

```{r}
nations <- read.csv("../Data/ClusrankNatvsWorld.csv")
colnames(nations) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations, alternative = "greater", method = "ds")
```

```{r}
nations_noprelim <- read.csv("../Data/Clusrank2019vs2022PrelimsOnly.csv")
colnames(nations_noprelim) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = nations_noprelim, alternative = "greater", method = "ds")
```
